The Astropy Project:

### 2017-09-29 main.tex
quantities
skycoord

The \texttt{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as a spherical (distance,
right ascension, declination) or Cartesian coordinates.
They can therefore be re-represented or transformed to other reference frames
(e.g., the Galactic frame) in an independent way.

@@

With all of that in mind, the typical user doesn't usually have to interact with
the \texttt{Frame} or \texttt{Representation} classes directly.

Instead, use the \texttt{SkyCoord} object...

>>>>

The \texttt{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \texttt{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as a spherical (distance,
right ascension, declination) or Cartesian coordinates.
They can therefore be re-represented or transformed to other reference frames
(e.g., the Galactic frame) in an independent way.

@@

The typical user doesn't usually have to interact with the \texttt{Frame} or
\texttt{Representation} classes directly.
Instead, \texttt{astropy.coordinates} provides a high-level interface to
representing astronomical coordinates through the \texttt{SkyCoord} class.
The \texttt{SkyCoord} class was designed to provide a single, go-to class that
accepts a wide range of possible inputs, and supports coordinate data in any
reference frame with a corresponding \texttt{Frame} class in any representation
with a corresponding \texttt{Representation} class.
